Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Final Draft - UNDER REVIEW}}

### 2015-04-02 Paper.tex
new gas costs

The application of rewards to a block involves raising the balance of the accounts of the coinbase address of the block and each uncle by a certain amount. We raise the block's coinbase account by $R_b$; for each uncle, we raise the block's coinbase by an additional $\frac{1}{32}$ of the block reward and the coinbase of the uncle gets rewarded depending on the block number. Formally we define the function $\Omega$:
\begin{eqnarray}
\Omega(B, \boldsymbol{\sigma}) & \equiv & \boldsymbol{\sigma}': \boldsymbol{\sigma}' = \boldsymbol{\sigma} \quad \text{except:} \\
\boldsymbol{\sigma}'[{B_H}_c]_b & = & \boldsymbol{\sigma}[{B_H}_c]_b + (1 + \frac{|B_\mathbf{U}|}{32})R_b \\
\forall_{U \in B_\mathbf{U}}: \\ \nonumber
 \boldsymbol{\sigma}'[U_c]_b & = & \boldsymbol{\sigma}[U_c]_b + (1 - \frac{1}{8} (U_i - {B_H}_i)) R_b 
\end{eqnarray}

@@

If RLP is used to encode a scalar, defined only as a positive integer ($\mathbb{P}$ or any $x$ for $\mathbb{P}_x$), it must be specified as the shortest byte array such that the big-endian interpretation of it is equal. Thus the RLP of some positive integer $i$ is defined as:
\begin{equation}
\mathtt{\tiny RLP}(i : i \in \mathbb{P}) \equiv \mathtt{\tiny RLP}(\mathtt{\tiny BE}(i))
\end{equation}

@@

\begin{tabular*}{\columnwidth}[h]{lrl}
\toprule
Name & Value & Description* \\
\midrule
$G_{step}$ & 1 & Default amount of gas to pay for execution cycle. \\
$G_{balance}$ & 20 & Paid for a {\small BALANCE} operation. \\
$G_{stop}$ & 0 & Nothing paid for the {\small STOP} operation. \\
$G_{suicide}$ & 0 & Nothing paid for the {\small SUICIDE} operation. \\
$G_{sload}$ & 20 & Paid for a {\small SLOAD} operation. \\
$G_{sset}$ & 300 & Paid for an {\small SSTORE} operation when the storage value is set to non-zero from zero. \\
$G_{sreset}$ & 100 & Paid for an {\small SSTORE} operation when the storage value's zeroness remains unchanged. \\
$G_{sclear}$ & 0 & Nothing paid for an {\small SSTORE} operation when the storage value is set to zero from non-zero. \\
$R_{sclear}$ & 100 & Refund given (added into refund counter) when the storage value is set to zero from non-zero. \\
$G_{create}$ & 100 & Paid for a {\small CREATE} operation. \\
$G_{createdata}$ & 5 & Paid per byte for a {\small CREATE} operation to succeed in placing code into state. \\
$G_{call}$ & 20 & Paid for a {\small CALL} operation. \\
$G_{exp}$ & 1 & Partial payment for an {\small EXP} operation. \\
$G_{expbyte}$ & 1 & Partial payment when multiplied by $\lceil\log_{256}(exponent)\rceil$ for the {\small EXP} operation. \\
$G_{memory}$ & 1 & Paid for every additional word when expanding memory. \\
$G_{txdatazero}$ & 1 & Paid for every zero byte of data or code for a transaction. \\
$G_{txdatanonzero}$ & 5 & Paid for every non-zero byte of data or code for a transaction. \\
$G_{transaction}$ & 500 & Paid for every transaction. \\
$G_{log}$ & 1 & Partial payment for a {\small LOG} operation. \\
$G_{logdata}$ & 1 & Paid for each byte in a {\small LOG} operation's data. \\
$G_{logtopic}$ & 1 & Paid for each topic of a {\small LOG} operation. \\
$G_{sha3}$ & 10 & Paid for each {\small SHA3} operation. \\
$G_{sha3word}$ & 10 & Paid for each word (rounded up) for input data to a {\small SHA3} operation. \\
$G_{copy}$ & 1 & Partial payment for {\small *COPY} operations, multiplied by words copied, rounded up. \\

>>>>

The application of rewards to a block involves raising the balance of the accounts of the coinbase address of the block and each uncle by a certain amount. We raise the block's coinbase account by $R_b$; for each uncle, we raise the block's coinbase by an additional $\frac{1}{32}$ of the block reward and the coinbase of the uncle by $\frac{15}{16}$ of the reward. Formally we define the function $\Omega$:
\begin{eqnarray}
\Omega(B, \boldsymbol{\sigma}) & \equiv & \boldsymbol{\sigma}': \boldsymbol{\sigma}' = \boldsymbol{\sigma} \quad \text{except:} \\
\boldsymbol{\sigma}'[{B_H}_c]_b & = & \boldsymbol{\sigma}[{B_H}_c]_b + (1 + \frac{|B_\mathbf{U}|}{32})R_b \\
\forall_{U \in B_\mathbf{U}} \; \boldsymbol{\sigma}'[U_c]_b & = & \boldsymbol{\sigma}[U_c]_b + \frac{15}{16}R_b
\end{eqnarray}

@@

If RLP is used to encode a scalar, defined only as a positive integer, it must be specified as the shortest byte array such that the big-endian interpretation of it is equal. Thus the RLP of some positive integer $i$ is defined as:
\begin{equation}
\mathtt{\tiny RLP}(i : i \in \mathbb{P}) \equiv \mathtt{\tiny RLP}(\mathtt{\tiny BE}(i))
\end{equation}

@@

\begin{tabular*}{\columnwidth}[h]{lrl}
\toprule
Name & Value & Description* \\
\midrule
$G_{zero}$ & 0 & Nothing paid for operations of the set {\small $W_{zero}$}. \\
$G_{base}$ & 2 & Amount of gas to pay for operations of the set {\small $W_{base}$}. \\
$G_{verylow}$ & 3 & Amount of gas to pay for operations of the set {\small $W_{verylow}$}. \\
$G_{low}$ & 5 & Amount of gas to pay for operations of the set {\small $W_{low}$}. \\
$G_{mid}$ & 8 & Amount of gas to pay for operations of the set {\small $W_{mid}$}. \\
$G_{high}$ & 10 & Amount of gas to pay for operations of the set {\small $W_{high}$}. \\
$G_{ext}$ & 20 & Amount of gas to pay for operations of the set {\small $W_{ext}$}. \\
$G_{sload}$ & 50 & Paid for a {\small SLOAD} operation. \\
$G_{jumpdest}$ & 1 & Paid for a {\small JUMPDEST} operation. \\
$G_{sset}$ & 20000 & Paid for an {\small SSTORE} operation when the storage value is set to non-zero from zero. \\
$G_{sreset}$ & 5000 & Paid for an {\small SSTORE} operation when the storage value's zeroness remains unchanged. \\
$R_{sclear}$ & 15000 & Refund given (added into refund counter) when the storage value is set to zero from non-zero. \\
$G_{create}$ & 32000 & Paid for a {\small CREATE} operation. \\
$G_{createdata}$ & 200 & Paid per byte for a {\small CREATE} operation to succeed in placing code into state. \\
$G_{call}$ & 40 & Paid for a {\small CALL} operation. \\
$G_{callvalue}$ & 9000 & Paid for a non-zero value transfer as part of the {\small CALL} operation. \\
$G_{callstipend}$ & 2300 & A stipend for the called contract subtracted from $G_{callvalue}$. Only applicable when the transferred value is non-zero. \\
$G_{callnewaccount}$ & 25000 & Paid for a {\small CALL} operation to a not previously excisting account. \\
$G_{exp}$ & 10 & Partial payment for an {\small EXP} operation. \\
$G_{expbyte}$ & 10 & Partial payment when multiplied by $\lceil\log_{256}(exponent)\rceil$ for the {\small EXP} operation. \\
$G_{memory}$ & 3 & Paid for every additional word when expanding memory. \\
$G_{txdatazero}$ & 4 & Paid for every zero byte of data or code for a transaction. \\
$G_{txdatanonzero}$ & 68 & Paid for every non-zero byte of data or code for a transaction. \\
$G_{transaction}$ & 21000 & Paid for every transaction. \\
$G_{log}$ & 375 & Partial payment for a {\small LOG} operation. \\
$G_{logdata}$ & 8 & Paid for each byte in a {\small LOG} operation's data. \\
$G_{logtopic}$ & 375 & Paid for each topic of a {\small LOG} operation. \\
$G_{sha3}$ & 30 & Paid for each {\small SHA3} operation. \\
$G_{sha3word}$ & 6 & Paid for each word (rounded up) for input data to a {\small SHA3} operation. \\
$G_{copy}$ & 2 & Partial payment for {\small *COPY} operations, multiplied by words copied, rounded up. \\
